---
title: "The Differences in Popular Musical Requiremnts between 3rd and 4th Generation Kpop Groups"
subtitle: "Groups are seperated further between girl and boy groups"
author: 
  - Oluwabusayomi Adekuajo 
thanks: "Code and data are available at: https://github.com/rubyzero10/Final_Starter_Fold.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Kpop has gained rapid popularity globally which is evident through setting new records and receiving public recognition on an international scale. This paper analyzes the possible changes in musicality represented in the shift between 3rd and 4th generation Kpop idols. Finidngs display that... Understanding current and evolving trends in this economically growing industry creates a plotform to predict popularity in groups to debute in the upcoming 5th generation. \\par \\textbf {Keywords:} music analysis, kpop, spotify, generational change"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)

#install.packages("spotifyr")
#install.packages("tidyverse")
#library(spotifyr)
#library(tidyverse)
#library(usethis)
```

# Introduction

Kpop has become a worldwide phenomenon with its groups constantly breaking new records on a global scale. What was once popular mainly in South Korean or Asian countries has found popularity amount the public with hybe continuously growing. The timeline of this growth can monitored through generations, for which there are currently four. The First Generation, which dates from the 1990s to the mid 2000s targeted mainly domestic and neighboring youth markets and consisted of family owned companies (cite) esiently it was the founding of such culture. During the second generation, things started to expand outside Korea as Youtube became popular early 2010 and international fans could be reached. This allowed for the starting target audience for third generation boy and girl group to be on an international scale involving social media platforms and streaming availability. From here on the large fanbase involved in Kpop can be seen across the nation and is it its peak currently in the 4th generation. Understanding the trends in music distinguishable between active generation of popular idols has insight to predict group popularity for the upcoming 5th generation. 

In this accelerating cycle, younger listeners, not only adopt particular songs or genres as badges of distinction and identity but also possess the discretionary income that will allow them to express their preferences and became a significant sector in the economy of music’s consumption (cite). In this paper, we analyze the title tracks of the 3rd generation and 4th generation Kpop groups which are amongst the most followed and popular on spotify. It is assumed that these groups will have the largest fan bases in the community, contributing the most to the economy along with attracting new fans to the genre as a whole. Top top 20 groups was present in raw data in which groups from all generation existed. 3rd and 4rd generation groups were selected from which they were further separated into boy girl group. This is due to different musical styles represented by each gender; the change in musical expression within each gendered group between the generation was also of interest. 


We find that, generally …  (have to finish making graphs find results)


The remainder of the paper is split into five sections. Section \@ref(data) explains data collection methodology, potential bias and ethics issues, as well as characteristics of selected data. Section \@ref(model) discusses the models used to produce results and investigate the transition of music between generation of kpop. Section \@ref(results)presents the findings from our methodology. Section \@ref(discussion) attempts to understand the results as well as explain the weaknesses and limitation in interpreting findings of the paper. It also showcases next steps to enhance and expand on the findings of the report


# Data

Our data is of K pop(Figure \@ref(fig:groups)).

```{r groups, fig.cap="Bills of penguins", echo = FALSE}

```



```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

```




# Model


# Results

# Discussion

## Consumption differences 


## The Role of Gender 

## International Influences 

## Weaknesses and next steps



\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References


